Analysis

### 2023-01-13 src/R/Analysis.Rmd
Resubmission -first commit

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(stringr)
library(GGally)
library(plotly)
knitr::opts_chunk$set(echo = TRUE)
```

@@

axisSize = 30
legendTitleSize = 30
legendTextSize = 28

@@

f2 = all %>% 
ggplot()+
  geom_boxplot(aes(x = flower_start, y = flower_length, fill = camCode, shape = camCode), size = 1) + 
  xlab("Onset of flowering (DOY)") + 
  ylab("Number of days flowering") +
    theme_bw()  +
  scale_fill_manual(name = "Camera ID",
                      values = c("gray26", "brown3", "dodgerblue3", "darkorange2", "chartreuse3"), aesthetics = c("colour", "fill")) + 
  scale_shape_manual(name = "Camera ID",
                      values = c(21,22,23,24,25)) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.title = element_text(size = legendTitleSize),
        text = element_text(size = axisSize),
        legend.text = element_text(size = legendTextSize),
        axis.line = element_line(),
        axis.text=element_text(colour="black"),
        panel.spacing = unit(0.7, "lines"))

ggsave("U:/BITCue/Projekter/TrackingFlowers/figures/OnsetVSLengthBox.png", f2, width = 15, height = 10)

# all %>% 
# ggplot()+
#   geom_point(aes(x = flower_start, y = flower_length, colour = CameraID))# +
# #geom_smooth(aes(x = flower_start, y = flower_length), method=lm)
#  
# t.test(nyaa04_meta$flower_length, nars13_meta$flower_length)

@@

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NYAA-04_AllCombinations.png', NYAA04_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NYAA-04_TenLowest.png', NYAA04_p2)

@@

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-13_AllCombinations.png', NARS13_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-13_TenLowest.png', NARS13_p2)

@@

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-04_AllCombinations.png', NARS04_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-04_TenLowest.png', NARS04_p2)

@@

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-17_AllCombinations.png', NARS17_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-17_TenLowest.png', NARS17_p2)

@@

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/THUL-01_AllCombinations.png', THUL01_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/THUL-01_TenLowest.png', THUL01_p2)

@@

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NYAA-04_AllCombinations.png', NYAA04_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NYAA-04_TenLowest.png', NYAA04_p2)

@@

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/THUL-01_AllCombinations.png', THUL01_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/THUL-01_AllZero.png', THUL01_p2)
```

@@

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-13_AllCombinations.png', NARS04_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-13_TenLowest.png', NARS04_p2)

@@

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-17_AllCombinations.png', NARS17_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-17_TenLowest.png', NARS17_p2)

>>>>

```{r setup, include=FALSE}

library(ggplot2)
library(dplyr)
library(stringr)
library(plotly)
library(GGally)

knitr::opts_chunk$set(echo = TRUE)
```

@@

axisSize = 34
legendTitleSize = 50
legendTextSize = 40

@@

#all = unique(all)

f2 = ggplot(unique(all), aes(x = camCode, y = flower_length, fill=camCode))+
  geom_boxplot() + 
  geom_point(position=position_jitterdodge()) +
  xlab("Onset of flowering (DOY)") + 
  ylab("Number of days flowering") +
  theme_bw()  +
  scale_fill_manual(name = "Camera ID", values = c("white", "white", "white", "white", "white"), aesthetics = c("colour", "fill")) +

  #scale_shape_manual(name = "Camera ID",
  #scale_fill_manual(name = "Camera ID", values = c("gray26", "brown3", "dodgerblue3", "darkorange2", "chartreuse3"), aesthetics = c("colour", "fill")) +

  #scale_shape_manual(name = "Camera ID",
   #                   values = c(21,22,23,24,25)) + 
  theme(legend.position = "none",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.title = element_text(size = legendTitleSize),
        text = element_text(size = axisSize),
        legend.text = element_text(size = legendTextSize),
        axis.line = element_line(),
        axis.text=element_text(colour="black"),
        panel.spacing = unit(0.7, "lines")) + 
  guides(fill = "none", color="none")

f2
ggsave("U:/BITCue/Projekter/TrackingFlowers/figures/OnsetVSLengthBox_withPoints.pdf", f2, width = 15, height = 10)

# all %>% 
# ggplot()+
#   geom_point(aes(x = flower_start, y = flower_length, colour = CameraID))# +
# #geom_smooth(aes(x = flower_start, y = flower_length), method=lm)
#  
t.test(nyaa04_meta$flower_length, nars13_meta$flower_length)

@@

#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NYAA-04_AllCombinations.png', NYAA04_p1)
#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NYAA-04_TenLowest.png', NYAA04_p2)

@@

#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-13_AllCombinations.png', NARS13_p1)
#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-13_TenLowest.png', NARS13_p2)

@@

#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-04_AllCombinations.png', NARS04_p1)
#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-04_TenLowest.png', NARS04_p2)

@@

#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-17_AllCombinations.png', NARS17_p1)
#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-17_TenLowest.png', NARS17_p2)

@@

#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/THUL-01_AllCombinations.png', THUL01_p1)
#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/THUL-01_TenLowest.png', THUL01_p2)

@@

#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NYAA-04_AllCombinations.png', NYAA04_p1)
#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NYAA-04_TenLowest.png', NYAA04_p2)

@@

#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/THUL-01_AllCombinations.png', THUL01_p1)
#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/THUL-01_AllZero.png', THUL01_p2)
```

@@

#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-13_AllCombinations.png', NARS04_p1)
#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-13_TenLowest.png', NARS04_p2)

@@

#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-17_AllCombinations.png', NARS17_p1)
#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-17_TenLowest.png', NARS17_p2)
